Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-06 paper/paper.qmd
Update
updated Cohen f

Since the interaction effect was not statistically significant ($p > 0.05$), we proceeded to assess the effect size with the purpose to evaluate the practical significance of our findings. Our model yields  $R^2 = 0.0398$. While $R^2$ commonly used in regression analysis to a measure explained variance, determining the goodness of fit of a model. However, in ANOVA Model the $R^2$ value doesn't have a direct interpretation as the proportion of variance explained by regression model and it also does not directly reflect differences between group means. We use the $R^2$ value to report the effect that corresponds to Cohen’s f guidelines i.e. $| f |$ is approximately 0.25 as our  $R^2$ falls between the small-medium categories.Even though the statistical test did not yield significant results, this quantity suggests we have a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

We did a post-hoc power analysis. Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's $f$ value of 0.204. This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

>>>>

Since the interaction effect was not statistically significant ($p > 0.05$), we proceeded to assess the effect size with the purpose to evaluate the practical significance of our findings. Our model yields  $R^2 = 0.0398$. While $R^2$ commonly used in regression analysis to a measure explained variance, determining the goodness of fit of a model. However, in ANOVA Model the $R^2$ value doesn't have a direct interpretation as the proportion of variance explained by regression model and it also does not directly reflect differences between group means. We use the $R^2$ value to report the effect that corresponds to Cohen’s f guidelines i.e. $| f |$ is approximately 0.20 as our  $R^2$ falls between the small-medium categories.Even though the statistical test did not yield significant results, this quantity suggests we have a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

We did a post-hoc power analysis. Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's $f$ value of 0.20. This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
